---
title: "examples"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
set.seed(2018-06-05)
```

The `trophic` package has several different uses. These are some examples of possible use cases. Please feel free to contribute your own additions (see [here](contribute.html) for details).

## example: predicting biomass of a high-order predator with known food web
```{r results="hide", warning=FALSE, error=FALSE, fig.width=10}  

# do something

```

## example: predicting biomass of a high-order predator with uncertain food web
```{r results="hide", warning=FALSE, error=FALSE, fig.width=10}  

# do something

```

## example: calculating sensitivity of predicted biomass to transfer efficiencies
```{r results="hide", warning=FALSE, error=FALSE, fig.width=10}  

# do something

```

## example: calculating sensitivity of predicted biomass to species' dominances
```{r results="hide", warning=FALSE, error=FALSE, fig.width=10}  

# do something

```
