---
output:
  html_document:
    theme: lumen
    highlight: default
    toc: false
---

<style type="text/css">
body{
  padding-top: 10px;
}
pre, pre:not([class]){
  font-size: 18px;
  color: #5a3a78;
  background-color: #f7f7f7;
  border: none;
}
.container-fluid {
    padding-left: 0;
    padding-right: 0;
}
.main-container {
    max-width: 2732px;
    margin-left: 0;
    margin-right: 0;
}
.bullet{
  color:#8960B3;
  font-size: 36px;
}
.resource,
.resource > p{
  color: #8960B3;
  font-size: 32px;
}
a, a:hover{
  color: #8960B3;
}
.col-md-4,
.col-md-5,
.col-md-6{
  padding-top: 25px;
  padding-bottom: 25px;
  padding-left: 25px;
  padding-right: 25px;
}
#header-content {
  max-width: 100%;
  margin: 0 auto;
}
#main-icon {
  width: 100%;
  height: auto;
  margin-right : auto;
  margin-left : auto;
  min-width : 210px;
  max-width : 585px;
  padding-left: 15px;
  padding-right: 15px;
  padding-top: 45px;
}
#main-icon-text{
  color:#ffffff;
  font-size: 24px;
  padding-left: 30px;
  padding-right: 30px;
  padding-bottom: 30px;
}
#panel1 {
  background-color: #f7f7f7;
  box-shadow: 0 0 7px 2px rgba(0,0,0,0.1);
  max-width: 90%;
  margin: 0 auto;
}
#bullets {
  padding-left: 15px;
  padding-right: 15px;
  font-size: 20px;
  text-align: center;
  max-width: 90%;
  margin-left: auto;
  margin-right: auto;
}
#example {
  padding-left: 15px;
  padding-right: 15px;
  font-size: 20px;
  max-width: 100%;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
set.seed(2018-06-05)
```

<div class="row">
<p id="main-icon-text">trophic models of ecosystem energetics in R</p>
</div>
    
</div>

</div>


<div id="bullets">

<br><br>

<div class="container">
<div class="row">

<div class="col-md-4">
  <p class="bullet"><b>simple</b></p>
  <br>
  models in trophic are modular and capture energy flows through food webs
</div>

<div class="col-md-4">
  <p class="bullet"><b>scalable</b></p>
  <br>
  trophic can run multiple scenarios in parallel
</div>

<div class="col-md-4">
  <p class="bullet"><b>extensible</b></p>
  <br>
  it's easy to develop your own modules to alter key components of trophic dynamics
</div>

</div>
</div>

<br><br>

</div>

<div id="panel1" class="resource">

<div class="container">

<br>

<div class="row">

<div class="col-md-1"></div>

<div class="col-md-5">
  <span class="fa fa-code fa-2x" style="vertical-align:middle;"></span> &emsp; <a href="#example">basic example</a>
</div>

<div class="col-md-1"></div>

<div class="row">

<div class="col-md-1"></div>

<div class="col-md-1"></div>

</div>

<br>

</div>

</div>



<div id="example">

<div class="container">

<br><br>

<h1 style="color: #8960B3;">basic example</h1>

<div class="row">

<div class="col-md-6">

Here's a simple example with the `mdb` food web included in trophic:

```
```
```
library(trophic)

food_web <- data(mdb)

food_web_object <- build_food_web(food_web)
plot(food_web_object)
```
```
trophic_object <- build_trophic_dynamics(food_web_object)
```
</div>
<div class="col-md-6">
```
production_estimates <- estimate_production(trophic_object)

```
```{r vis, echo=FALSE, eval=TRUE, results='hide', message=FALSE, warning=FALSE, fig.height=4, fig.width=6, fig.align="center"}

library(trophic)

food_web_object <- build_food_web(food_web)
plot(food_web_object)

trophic_object <- build_trophic_dynamics(food_web_object)

production_estimates <- estimate_production(trophic_object)
```

</div>
</div>

<br>

</div>
</div>
